A general Nullstellensatz for generalized spaces

### 2019-05-08 paper-qcoh.tex
Subtopos case finished

% XXX The internal statement occurring in Theorem~\ref{thm:quasicoherent} is
% higher-order, therefore

\begin{cor}Let~$\TT'$ be a quotient theory of~$\TT$, not necessarily Horn.
Assume that the generic model~$U_\TT$ is a sheaf for the topology
on~$\Set[\TT]$ cutting out the subtopos~$\Set[\TT']$. Then, from the internal
point of view of~$\Set[\TT']$, the canonical map~$A \to (U_{\TT'})^{\Spec(A)}$
is an isomorphism of~$U_\TT$-algebras for every finitely
presented~$U_\TT$-algebra~$A$. (By~``$\Spec(A)$'', we mean the set
of~$U_\TT$-algebra homomorphisms from~$A$ to~$U_{\TT'}$.)
\end{cor}

>>>>

\begin{thm}Let~$\TT'$ be a quotient theory of~$\TT$, not necessarily Horn.
Assume that~$U_\TT$ is a sheaf for the topology
on~$\Set[\TT]$ cutting out the subtopos~$\Set[\TT']$. Then, from the internal
point of view of~$\Set[\TT']$, the canonical map~$A \to (U_{\TT'})^{\Spec(A)}$
is an isomorphism of~$U_\TT$-algebras for every finitely
presented~$U_\TT$-algebra~$A$. (By~``$\Spec(A)$'', we here mean the set
of~$U_\TT$-algebra homomorphisms from~$A$ to~$U_{\TT'}$.)
\end{thm}

\begin{proof}In general, the generic model~$U_{\TT'}$ is the sheafification
of~$U_\TT$~\cite[Lemma~2.3]{caramello:definability}. By the sheaf assumption,
the objects~$U_{\TT'}$ and~$U_\TT$ actually agree as functors
on~$\Mod{\TT}_\mathrm{fp}$.

Following the Kripke--Joyal translation of the claim, similar as in the proof
of Theorem~\ref{thm:quasicoherence}, it suffices to show that
applying the sheafification functor to the isomorphisms provided by
Lemma~\ref{lemma:fp-double-dual} (over arbitrary slices) results in
isomorphisms of the same form. This fact follows from the lemma (applied twice)
that computing the internal Hom to a sheaf commutes with sheafification and
from the observation that the construction~``free~$U_\TT$-module modulo
relations'' is geometric, hence in particular commutes with sheafification.
\end{proof}
